Investigating soundscapes perception through acoustic scenes simulation

### 2018-09-04 lafaySimulatedScenePerception.tex
fixing typo

Accounting for the previously detailed perceptual matters, two taxonomies are built, one for sound events and one for sound textures. Up to four levels of abstraction are considered from the most generic classes(level 0) to the most specific classes (level 3), leading to a taxonomy close to the one used in~\cite{Salamon14}, see Appendix~\ref{app:taxonomie}. Only three levels of abstraction are considered for the texture sounds, see Figure~\ref{fig:taxonomieT}.

>>>>

Accounting for the previously detailed perceptual matters, two taxonomies are built, one for sound events and one for sound textures. Up to four levels of abstraction are considered from the most generic classes (level 0) to the most specific classes (level 3), leading to a taxonomy close to the one used in~\cite{Salamon14}, see Appendix~\ref{app:taxonomie}. Only three levels of abstraction are considered for the texture sounds, see Figure~\ref{fig:taxonomieT}.
